Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-21 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Title ideas?

\begin{document}
\title{A graph-based data model for interactive 
evolutionary computation}

@@

@@

\subsection{Set-up}
\label{sec:setup}

>>>>

\begin{document}
% Title ideas here:

\title{Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution}

@@

There is information regarding users and their collaborations, the interaction and subjective evaluation of individuals of the population. There is also information about the actual evolutionary process: relationships between individuals and evolutionary operators, used.

@@

\subsection{Set-up}
\label{sec:setup}
% Anuncements
% Table of GA Parameters
% Time
